Methods for Large Scale Learning to Rank

### 2014-03-12 report/Chapters/RelatedWork.tex
tweede relevante forward search resultaat beschreven

\subsection{Stacked generalisation}
% TODO: Kijken naar deze subsection, is erg zwak %
A \ac{DSN} is a processing architecture developed from the field of \emph{Deep Learning}, that uses the \ac{MSE} loss function that is easily optimisable. \ac{DSN} is based on the stacked generalization ensemble learning method \cite{Wolpert1992}, an approach where several learning models are stacked on top of each other in such a way that the output of a model is used as one of the input features of models higher up in the stack. Each layer in the stack learns has the task of learning the weights of the inputs of that layer. The close-form constraints between input and output weights allow the input weight matrices to be estimated in a parallel manner. Deng et al. \cite{Deng2013} % TODO: beschrijven Deng et al.%\\

>>>>

\subsection{Stacked generalisation}
% TODO: Kijken naar deze subsection, is erg zwak %
A \ac{DSN} is a processing architecture developed from the field of \emph{Deep Learning}, that uses the \ac{MSE} loss function that is easily optimisable. \ac{DSN} is based on the stacked generalization (stacking) ensemble learning method \cite{Wolpert1992}, an approach where several learning models are stacked on top of each other in such a way that the output of a model is used as one of the input features of models higher up in the stack. Each layer in the stack learns has the task of learning the weights of the inputs of that layer. The close-form constraints between input and output weights allow the input weight matrices to be estimated in a parallel manner. Deng et al. \cite{Deng2013} % TODO: beschrijven Deng et al.%\\

\subsection{Randomisation}
Most ensemble learning based Learning-to-Rank methods are based on boosting. Although boosting have shown to be an effective method in Learning-to-Rank, it has the drawback that the models in the ensemble are not completely mutually independent, which makes the process harder to parallelise. Geurts and Louppe \cite{Geurts2011} propose a tree based ensemble method in which the trees are build using random subsets of the available features. The authors called this method \ac{ET} and originally proposed this method for classification and regression settings instead of ranking settings \cite{Geurts2006}. The \ac{ET} algorithm is similar to the well-known Random Forest algorithm, with two differences: 1) in \ac{ET} each tree is build on the complete dataset instead of random subsets of the data and 2) \ac{ET} sets the discretisation thresholds that define the splits in the tree randomly, instead of based on the sample. The randomisations in the process make the models in the ensemble mutually independent, which makes it trivial to parallelise by training each tree on a different node. In contrary to what one might think, \ac{ET}s show very good performance on benchmark data with a 10th place in the Yahoo! Learning to Rank Challenge.\\
